Thank you so much for taking the time to contribute in to htop!

\subsection*{Bug Reports }

Bug reports should be posted in the \href{https://github.com/htop-dev/htop/issues}{\tt Github issue tracker}. Bug reports are extremely important since it\textquotesingle{}s impossible for us to test htop in every possible system, distribution and scenario. Your feedback is what keeps the tool stable and always improving! Thank you!

\subsection*{Pull Requests }

Code contributions are most welcome! Just \href{https://github.com/htop-dev/htop}{\tt fork the repo} and send a \href{https://github.com/htop-dev/htop/pulls}{\tt pull request}. Help is especially appreciated for support of platforms other than Linux. If proposing new features, please be mindful that htop is a system tool that needs to keep a small footprint and perform well on systems under stress -- so unfortunately we can\textquotesingle{}t accept every new feature proposed, as we need to keep the tool slim and maintainable. Great ideas backed by a PR are always carefully considered for inclusion though! Also, P\+Rs containing bug fixes and portability tweaks are always included, please send those in!

\subsection*{Feature Requests }

Please label Github issues that are feature requests with one of the {\ttfamily feature request} labels. If you can\textquotesingle{}t do this yourself, don\textquotesingle{}t worry. The friendly folks from the core team will distribute and fixup Github labels as part of the regular reviews.

\subsection*{Style Guide }

To make working with the code easier a set of guidelines have evolved in the past that new contributions should try to follow. While they are not set in stone and always up for changes should the need arise they still provide a first orientation to go by when contributing to this repository.

The details of the coding style as well as what to take care about with your contributions can be found in our \hyperlink{styleguide_8md}{style guide}. 